%!TEX root = ../notes.tex
\section{January 31st}

Double-sided history - humans decide what takes shape as history

\subsection{Unpacking Citizenship}
The nightmares of equal citizenship
Linda Kerber - ``braided citizenship''

How does one become a citizen?
\begin{itemize}
  \item Birth
  \item Parents citizens
  \item Naturalization 
\end{itemize}

The promise of citizenship: rights/privileges

Concepts/Terms:
\begin{itemize}
  \item Jus Soli
  \item Jus Sanguinis
  \item Civil/Political/Social Citizenship
  \item Coverture
\end{itemize}

\paragraph{Aristotle's Politics (350 BCE)} Human beings are by nature social, so they will form states. A good state maximizes health/safety/success of its citizens. Citizenship is about active participation.

\paragraph{The Body Politic} State analogous to human. Hierarchy of interdependent parts 

\paragraph{Aristotle, ``The Generation of Animals''} Early understanding of human reproduction. Science and politics tied together. Residue of these ideals in contemporary world. Men active/women passive.

\paragraph{Social citizenship} Understanding how we belong to a society/collective

\paragraph{T.H. Marshall - 3 pillars of citizenship} Civil citizenship (legal rights). Political citizenship (voting, holding office, \textit{active} participation). Social citizenship (basic liberties). The disenfranchisements of felons circumvents political citizenship. Labeling people of color ``criminals.''

Conflict between civil/political and social citizenship. Protection from workplace dangers (social citizenship). Muller v. Oregon (1908), women were disallowed from working as many hours (violation of civil citizenship). Why not protect men as well as women? Men thought to be sovereign, not dependent, not propogating citizenry.

Who was under this protection? White women (did not intervene in the case of African American women).

\paragraph{Castle doctrines} People can protect themselves with lethal force on property. At odds with states' desire to stop domestic violence.

\paragraph{Couverture} Women's citizenship rights derive from father or husband. Many overturned in 19th c. but effects late into 20th c. (laws preventing women from signing for credit cards).

\paragraph{Vagrancy laws} If non-white, not working for white man, labeled a ``vagrant.'' Immigrants could be discharged (criminalization of poverty)