%!TEX root = ../notes.tex
\section{February 11th -- Histories Hidden in Plain Sight}

See how certain assumptions taken for granted by large groups change over time. In readings this week. What do these histories of evolutions of assumptions mean for citizenship and belonging?

Today: thinking about how some of these hidden histories are closer than we might think.

Historical amnesias: sometimes intentional, sometimes unintentional forgetting of unpleasant facts

\paragraph{Paul Revere} Famous poem from 1860 by Longfellow. Midnight ride marking beginning of military engagement of Revolutionary War. Has been held up as example of patriotism that freed US.

Mark and Philis, servants of John Codman. Killed and hung in Gibbet (iron chains), as an example to other enslaved people, for 20 years. Paul Revere rode past `Mark in chains' -- a landmark.

Connecticut didn't completely outlaw slavery until 1848. Not all northern states were on the same page.

\paragraph{Thomas Jefferson} Eugene Foster, pathologist who searched for genetic link between descendants of Thomas Jefferson and his slave Sally Hemings. Found link in 1998.

No documentation of Sally Hemings. No actual words, only their descendants. A pathologist comes out with these findings, a film comes out 2 years later to make sense of this relationship.

Thomas Jefferson wrote the Declaration of Independance. Excelled in many different fields. Freed seven of his slaves, all members of Hemings family. Not mentioned in official biography, Sally and her children listed amongst his possessions.

Member of Anti-federalist party, but acquired Louisiana in 1803. Did some major things to expand the size and power of the US.

\paragraph{Republican Motherhood} Thinking about the emergence of `civil citizenship.' People declaring their citizenship/belonging through the courts. What about `political citizenship?' Could everyone vote? Free women were citizens, but demonstrated their citizenship in the home. Remained to provide care, educate the next generation. 

In Virginia, laws in 1660s say that all children born to enslaved women are enslaved. Age of consent laws protect only white girls. Missouri -- any woman can use lethal force to protect herself from sexual violation. In 1840s, enslaved woman kills her master defending herself, but is found guilty of murder and executed. Even if race wasn't written into laws, the way in which they were applied reinforced the second class citizenship.

Rumors started in 1802 about Jefferson, taken hold of by opposition party (in effort to prevent his reelection). He was reelected anyway, but discontent spread. Scandal not about being unmarried to Hemings, or allowing his children to be enslaved, but rather that he would be critical of slavery and still own slaves.

Clotel: invention based on Sally Hemings' story.