%!TEX root = ../notes.tex
\section{March 4th -- The Queer Career of Jim Crow: Scientific Racism, Sexology, and the Politics of Pathology}

Prof. Somerville's essay provides examples: 1875 Page age prohibits the immigration of Chinese women ``for purposes of prostitution.'' Racialized and sexualized assumptions. Ratio of Chinese men to women was 20:1 at the time it was passed.

State is trying to prohibit asian family from taking root. Asian citizenship is being curtailed.

Photo of completion of trans-continental railroad depicts all white workers. Visual silence -- Chinese workers made invisible by their absence.

\paragraph{Civil Rights amendments} 13th/14th/15th amendments. 14th amendment: emergence of \text{jus soli}, conferring of voting rights (political citizenship) to African American men. Do these laws create racial equality?

Rutherford B. Hayes withdraws forces from Confederacy, states begin to pass laws that inhibit the political/civil citizenship rights. Poll taxes, grandfather clauses -- effect, even if not mentioning race, is to exclude African Americans from citizenship.

\paragraph{Jim Crow} Jim Crow laws create separate spaces, where they are not supposed to mix. Happens in north as well as south (predominant in south).

Plessy v. Ferguson 1896 -- Supreme Court rules that seperate but equal (system of Jim Crow segregation) laws are legal.

Growth of extreme racist violence. Blackface performance teaches the population about the ideas underlying Jim Crow laws.

\paragraph{Birth of a Nation} Highest grossing film of its time. First film screened in the white house. Truillot's retrospective significance -- African American rule and chaos in the south after the Civil War. Depiction of the Civil War/outlawing of slavery creating chaos. Inaccurate history steeped in the politics of the 20th century. Reaffirms notion that violence is necessary to contain African Americans since slavery is no longer able to do so.

Emergence in 19th c. of science as way of categorizing/organizing/learning about human body, replacing church. The idea that science is objective/neutral. Libertory biologism -- belief that science is going to rescue humankind from what ails it.

\paragraph{Scientific racism} Belief that maintining the purity of whiteness is essential to the safety and quality of society.

Invoking scientific though that African Americans need to be excluded from citizenship.

\paragraph{Eugenics} Not enough white people propogating citizenry, too much immigration. Theodore Roosevelt coine term ``race suicide.'' Duty of white middle class to produce more offspring -- patriotic. Dillingham commision report is example of state's effort to gather data on reproduction rate of immigrants.

Popular literature emerges steeped in the idea that reproduction of certain parts of the population need to be curtailed. Calling it ``scientific racism'' today distances us from this. Many prominent feminists bought into Eugenics movement -- argued that more women need access to information about how their bodies work, safe and reliable birth control. Built into this was idea that birth control would limit reproduction of ``inferior stock.''

Detection of difference on the pathologized body -- e.g. immigration officials detecting undesirable immigrant and excluding admission. \textbf{LPC}: Likely to become a Public Charge. Deciding who will/will not become independent, self-sustaining citizen.

\paragraph{Sexology} detectable difference etched on human body. Similarly pathologizing. Church and courts mandated against criminal sex acts. Spreading idea that non-procreative sex should be punished.

Categories of sexual anomoly emerge. The ``invert'' doesn't perform their gender correctly. A whole proliferation of particularly pathologized human behavior.

Havelock Ellis (1859-1939) most prominent in discussing homosexuality. Refers initially to behavior, rather than a category of a person. Ellis categorized this as biologically inherited. Expand rights for minoritized by saying it isn't chosen, but true by nature. Using science to argue that it shouldn't be criminalized.

Reasoning may seem liberatory, but may create pity rather than accepting. Other sexologists depict inversion as a sign of hereditary weakness/disintegration.

Elizabeth Cady Stanton. 15th amendment fails to mention sex as factor exclusion. In 14th amendment, women are definitely considered citizens (born on U.S. soil). 1872, Virginia Minor tries to register to vote in Missouri. 1874 decision -- women may be citizens, but suffrage is not universal right of citizenship. Federal govt leaves it up to individual states to decide the matter. Working in conjunction with Jim Crow laws to dictate access to the vote.

\paragraph{``The Women Question''} Much concern about what will happen if women start to vote. Idea that they will become less feminine if they step outside their space (inversion). Strict bifurcation in terms of gender. Quote in Gardner: a woman is not just an individual.

\paragraph{Derivative Citizenship} Women's citizenship derived from relationship to a man. Couverture: notion that women's civil/political citizenship derives from father, then husband when married.
