%!TEX root = ../notes.tex
\section{April 1st -- War Brides and Prostitutes: Sex and Wartime Citizenship}

State's obsession with the nation's sexual hygiene escalates during wartime.

\paragraph{Comstock Laws} Police Inspector Anthony Comstock -- crusader against ``obscenity''. Margaret Sanger were jailed for distributing information about reproductive health. Devices marketed as hygiene products. Comstock laws overturned in 1960s for married couples, completely revoked in 1972. Contributes to shame about sexual health.

Intense fear of STDs, especially during wartime. Controlling STDs of men in service. United States advocated abstinence. Condoms were legalized afterwards in US (1918).

Ideas of controlling population through selective breeding was considered progressive. Widespread fear of unfit breeders. 

\paragraph{Buck v Bell} State's investment in compulsory sterilization. Started with Indiana in 1907. Carrie Buck was determined to be ``feeble-minded'', as well as her mother and daughter. Upholds sterilization, disproportionitely harms minorities and lower classes.

\paragraph{Tuskegee Experiment} Between 1932 and 1972, recruited 399 African American sharecroppers who already had syphilis, promised them meals, transportation, burial service. Watched how the body responded, but they did not treat them (pencillin actively withheld). 1972 was key year in exposing the state's complicity in such things. Reason for informed consent now. 250 of these men registered for the draft in WWII. Normally, STDs exclude one from service, but an exception was made.

Going back to T.H. Marshall's three ``branches'' of citizenship (1950). Civil, political, and social. Civil is most basic -- the way citizens obtain rights through the courts. Political -- how to participate in representative government. Social -- based on idea that federal government needs to protect public welfare.

\paragraph{Welfare State} Creation of welfare state and expansion of social citizenship in 20th century. Great Depression starting in 1929, continues through 1930s. Depression was international, ended by WWII.

FDR introduces New Deal in 1933. Relieve the depression through Relief, Recovery, and Reform. Designed to restore citizen's faith in the seemingly failed state apparatus. Protect unions, regulate hours that all can work, make workplace safe. Expansion of state apparatuses of power.

\paragraph{The Bracero Program} 4 million people from Mexico immigrated from 1942-1964 for agricultural work in Southwest. Collusion between US and Mexican government to fill labor gap created by WWII. Originally run by individual US farmers during WWI, no real government oversight.