%!TEX root = ../notes.tex
\section{April 10th -- Hybrid Histories \& Colorblind Commemorations: Legacies of Blackface}

Three different narratives coming through blackface minstrelsy.

\begin{itemize}
	\item Narrative of assimilation. Seeing how groups that possess ``provisional whiteness'' were able to whiten themselves as they performed physical blackness of others. Emphasizes physical difference, racial ``othering'' at its most powerful/persuasive.
	\item Based on mythology of harmonious race relations. African Americans portrayed as happy-go-lucky, unaware of violence, childlike.
	\item Minstresy based on belief in two things that sound difficult to reconcile: belief in intrinsic race difference, that holds blacks to be physically different, unassimilable; appreciation of black culture.
\end{itemize}

Resistance in 1950s of explicit blackface performance. State's erosion of biological racial exclusions seen in culture as well. However, minstrelsy does not go away -- it just changes form. In 1940s/50s, race minstrelsy takes on different forms that undermines cultural citizenship of African Americans or others.

Thinking about covering -- what happens when historical moments are downplayed or hidden? Jolson's blackface performance made him truly American. The statue on his shrine is a small example of how historical memory can shift/how it can be silenced.

Even romantic racialism has an impact on how people are percieved as citizens. Uncle Remus from Disney's ``Song of the South'' in 1946. Tells happy stories of the good old days, kindly old black man.

\paragraph{Colorblindness} Defined by Ian Haney Lopez. The definition is on a slide. Related to: Passing -- hiding the visibility of a certain trait. Covering -- downplaying a trait, minimizing its obtrusiveness (downplaying vs. hiding). Cotes' article is about covering -- President Obama's attempt to downplay his own blackness, by not talking about racial issues. Attempting to solve racial problems by not talking about them, which has consequences.

Strong strain of psychiatry that suggested that homosexuals needed to ``convert.'' Electroshock therapy/lobotomy performed. Considered a mental disorder until 1973(?).

``Mongolian'' category divided in WWII when Japanese Americans were detained. Given \$25 and a train ticket to go home. 1980s, Jimmy Carter launched investigation, reparations given to families. In 1950s onward, incredible popular resistance to various forms of state expulsion and exclusion on racial fronts.