%!TEX root = ../notes.tex
\section{April 15th -- title}

Richard Rodriguez: Nixon created ``Hispanic'' in directive \#15 (1972). Categorizes ethnicities, adds ``Hispanic'' as way of uniting people of nations formerly colonized by Spain who otherwise have nothing important.

How the private sphere frames public policies about how people belong.

Covering: survival strategy to downplay their unacceptable traits to be more acceptable in dominant society.

Three tools from Foucault:
\begin{itemize}
	\item Periodization -- the periodization of sexuality. The emergence of sexological sciences in 19th century, transition from set of outlawed acts to set of ideas about intrinsic sexual identity. (e.g. the Invert) 
	\item Power -- power is diffused. Not concentrated in one location, spread throughout the nation through citizens, who have form of self-policing more effective than state domination. Wherever there is domination, there is resistance.
	\item Biopower -- where the government becomes focused on how to produce the best possible citizenry. Inventing new categories of race, keeping tabs on self-identification, protecting certain populations.
\end{itemize}

Legacies of eugenics of the state. How does the state shape family structures in the face of certain ideals of national belonging? Sterilization primary affected non-white women. 

\paragraph{Fannie Lou Hamer} African American woman, leader of Student Nonviolent Coordinating Committee. 1917-1977, in 1961 became one of approximately 65k people sterilized without consent.

\paragraph{Stratified reproduction} The idea that some women are a reproductive threat to the nation, whose reproduction has to be curtailed or disincentivized.

Family at the top gets tax deduction for each child. State incentivizes this type of reproduction. Also tax credit for childcare expenses. Modern eugenics: emphasis on reproducing wealth.

\paragraph{Child Citizenship Act of 2000} Streamlines adopting process for U.S. citizens. Makes it easier for people with resources to pay for transnational adoption.

At Harvard, ads at fertility clinic seeking eggs. Assumption of certain racial/ethnic categories being prioritized.

In 2007, overseas Filipinos sent home 14 billion (?) dollars. Not encouraged to bring their children.

\paragraph{CA Proposition 187, AZ Senate Bill 1070}  Deny public benefits to unauthorized migrants in California. Arizona -- attrition through enforcement. Create hostile environment to make problem go away.