%!TEX root = ../notes.tex
\section{April 22nd -- Neo-liberalism todo... }

\paragraph{Straified reproduction} Some forms of reproduction are despised and held suspect. Chavez reading. Belief that Latina women have higher reproduction rate, use of social services, when really the rates are no different.

Sterlization serving the interest of stratifid reproduction, especially against women of color.

The pill -- approved in 1960s. Developed in 1950s amongst heightened anxiety about percieved threat of overpopulation. First large clinical trials on United States citizens in Puerto Rico. Many horrific life-threatening side-effects. Five participants died, no effort made to determine cause of deaths (did pill cause them?). By 1963, 2.3 million using pill. Wasn't actually legalized until 1965 for married women. Griswold v. Conn. protected \textit{marital} privacy.

1964 report by Senator Moynihan about cycle of dependency in black families upon welfare. Disintegration in second half of 20th century to social citizenship. Withdrawing support for citizens, increasing support abroad in military action. Individual and free market partnered in responsibility for citizenry.

Pushback against neo-liberalism? Obama's healthcare plan, staunch opposition. Undermining of personal responsibility, self-care. 

\paragraph{Self-care} Weber argues that neo-liberal mandate for care of the self influences Makeover TV. Genre focuses on experts coming in and training the before body, up to individual in the end to maintain his/her new look.

How does the diffusion of power affect those with non-normative sexualities? Weber believes that queerness is accepted if it advances heteronormative relationships.

Spectacularization of women's bodies to sell products. Women get recruited as consumer representatives for their families. 1963, the Feminine Mystique by Betty Friedan -- housewives buy things for the house. Commodities used to make women feel more confident -- advertisers channeling women's guilt by making women feel like experts about choosing products.

Nation's continued love affair with racial difference (from the time when blackface was a very popular form of entertainment) seen in commodification of racial differences. Made marketable.

What gets veiled when nation stands up to protect certain citizens against others?